Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-17 content/background.tex
inter- and intra-procedural to interprocedural and intraprocedural

\subsection{Terminology and Notation}
%We will start by introducing several concepts used by the IFDS and IDE analyses.
%\begin{mdelete}\mtodo{We already say (but less precisely) what a CFG is in the introduction.}
The \textit{control-flow graph} of a procedure is a directed graph whose nodes are instructions, and which contains an edge from $n_1$ to $n_2$ whenever
$n_2$ may execute immediately after $n_1$. A CFG has a distinguished \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$.
Following the presentation of \cite{reps1995precise,sagiv1996precise}, we follow every
call instruction with a no-op instruction, so that every \textit{call node} is immediately
followed by a \textit{return node} in the CFG.
%\end{mdelete}
%and edges represent transfer of control between the instructions during an execution of the program. 
%A control-flow graph has a unique start node, $\startmain$, which is the node corresponding to the program entrypoint.
%An \textit{intra-procedural} path is a path in a control-flow graph whose nodes are in the same procedure. By contrast, an \textit{inter-procedural path} is one that contains nodes from different procedures. 
The \textit{control-flow supergraph} of a program contains the CFGs of all of the procedures as
subgraphs. In addition, for each call instruction $c$, the supergraph contains a \textit{call-to-start} edge to the start node of every procedure that
may be called from $c$, and an \textit{end-to-return} edge from the end node of the procedure back to the call instruction.
%\otodo{do we really need to extra "return nodes" that the IFDS/IDE papers add?}
%is a control-flow graph
%in which each procedure $p$ is augmented with an additional \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$, and for each call $c_q$ to a procedure $q$, there is a \textit{call node} \textsf{call}$_{c_q}$ and subsequent \textit{return node} \textsf{return}$_{c_q}$.

%A control-flow supergraph allows us to model the control flow in inter-procedural paths.
 %The flow from the caller to the callee is represented using an edge \[(\textsf{call}_{c_q},\,\textsf{start}_q)\,.\] The control flow from the callee back to the caller goes through an edge \[(\textsf{end}_q,\,\textsf{return}_{c_q})\,.\]

@@

%arrow description
    \node [description] (intra_arrow_left) [above right = \dist and 2*\dist of st_secret] {};
    \node [description] (intra_arrow_right) [right = \dist of intra_arrow_left] {};
    \node [description] (inter_arrow_left) [below = .5*\dist of intra_arrow_left] {};
    \node [description] (inter_arrow_right) [below = .5*\dist of intra_arrow_right] {};
    \path[->](intra_arrow_left) edge node[right = .5*\dist]{intra-procedural edge} (intra_arrow_right);
    \path[dashed,->](inter_arrow_left) edge node[right = .5*\dist]{inter-procedural edge} (inter_arrow_right);
\end{tikzpicture}
}
  \caption{An example supergraph for Listing~\ref{list:examplejava}}%
  \label{fig:examplesupergraph}%
  \end{figure}
\end{example}
}

@@

%Let each call node in a program be labeled with a distinct opening parenthesis and the corresponding return node with the matching closing parenthesis. For a given path $p$, let $s$ be the string that is obtained by concatenating the labels of the nodes in $p$.
%Then $p$ is \textit{valid} if $s$ belongs to the language of substrings of balanced parentheses. The set of all inter-procedurally valid paths from the start node to a node $n$ is denoted as $\ivp(n)$. The set $\ivp(n)$ is a conservative approximation of all concrete execution paths from the start node to $n$.

%A \textit{context-sensitive} data-flow analysis is an analysis that considers only inter-procedurally valid paths.

@@

However, the graph also contains an inter-procedurally invalid path
  \[
    p_2=\left[\highlight{\textsf{call}_\texttt{f}}{lightsalmonpink},\,
          \highlight{\textsf{start}_\texttt{f}}{lightsalmonpink},\,
          \highlight{\texttt{if (s == null)}}{lightsalmonpink},\,
          \highlight{\texttt{return s}}{lightsalmonpink},\,
          \highlight{\textsf{end}_\texttt{f}}{lightsalmonpink},\,
          \highlight{\textsf{return}_\texttt{A.f}}{greyblue}
    \right]
  \]
  with corresponding string $\langle\}$.
\end{example}
\end{mdelete}
}

@@

\subsection{IFDS}\label{sec:bgifds}
The IFDS framework~\cite{reps1995precise} is a precise and efficient algorithm for data-flow analysis
%. IFDS was developed in 1995 by T.\,Reps, S.\,Horwitz, and M.\,Sagiv at the University of Wisconsin and
that has been used to solve a variety of data-flow analysis problems~\cite{bodden2013spl,naeem2008typestate,DBLP:conf/birthday/KreikerRRSWY13,tripp2009taj}.
%\mtodo{ The four references take away space in the References section. Remove some of them?  }
The IFDS framework is an instance of the \textit{functional approach} to data-flow analysis~\cite{pnueli1981two}
because it constructs summaries of the effects of called procedures.
\commentout{The IFDS analysis is a version of the classic \textit{functional approach} to data-flow analysis proposed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}.}
\commentout{In other data-flow algorithms not based on the functional approach, the result of the analysis at the entry of a procedure ``merges'' the incoming data obtained from all callers of the procedure. As a consequence, there is one global data-flow result computed at the end of the procedure. Context-sensitivity, however, allows an analysis to compute the data-flow result for a given procedure as a \textit{function} of the data-flow value at the start of the procedure. 
In other words, the analysis result for a procedure varies depending on where the procedure was called from. This significantly improves the precision of a data-flow analysis, which is why context-sensitivity is an important advantage of IFDS over classic data-flow algorithms.}
The IFDS framework is applicable to \textit{inter-procedural} data flow problems whose domain is \textit{subsets} of a \textit{finite} set $D$,
and whose data-flow functions are \textit{distributive}.
A function $f$ is distributive if 
$f(x_1\sqcap x_2)=f(x_1)\sqcap f(x_2)$.

%The IFDS algorithm is applicable to problems which can be expressed with data-flow functions that satisfy certain restrictions. \textit{Inter-procedural} flow functions specify how data flows from the invocation of a procedure to its start, and from the procedure's end back to its call site. \textit{Distributive} flow functions are those that distribute over the confluence operator. In the context of IFDS, the confluence operator is called meet, and it can be either union or intersection. The data-flow facts on which the analysis operates must be a \textit{finite} set $D$. Each flow function operates on a \textit{subset} of $D$ (for example, the set of variables in the program) which makes the domain of the flow functions the power set of $D$.

\commentout{The purpose of the IFDS framework is to solve a special subset of inter-procedural, flow-sensitive, context-sensitive data-flow-analysis problems. The main idea of IFDS is to encode the data-flow analysis problem into a graph-reachability problem.}

@@

The flow functions $F$ define the edges of the exploded supergraph.
Using the flow functions, the IFDS algorithm computes the inter-procedurally \textit{realizable} paths from the start to the rest of the exploded graph's nodes. A realizable path is a valid path in the exploded supergraph that starts with the entry node $\startmain$.

@@

The IDE framework is an expressive extension to IFDS that was created by the same authors in 1996.
The problems that IDE can solve include, but are not limited to, IFDS problems~\cite{reps1995precise}. Just as the IFDS algorithm, the IDE algorithm is suitable for data-flow analyses that can be encoded with inter-procedural, distributive flow functions. However, in IDE, the domain of the flow functions is not restricted to sets $D$ of data-flow facts. The IDE domain of a flow function consists of \textit{environments} that map data-flow facts from the set $D$ to lattice elements.

@@

The IDE algorithm~\cite{sagiv1996precise} extends IFDS to
\textit{inter-procedural} \textit{distributive} \textit{environment}
problems. An \textit{environment} problem is an analysis whose dataflow
lattice is the lattice $\textsf{Env}(D,L)$ of maps from a finite set $D$ to a meet semilattice
$L$ of finite height, ordered pointwise. Like IFDS, IDE requires the dataflow functions to be distributive.

@@

\mtodo{I think the rest of this section will not make sense to anyone who does not already understand it. Should I try to replace it with one paragraph that tries to give an intuitive understanding of what the IDE algorithm is doing?}
The overall idea behind computing the lattice elements $l_{n,\,d}$ is the following. For each inter-procedurally realizable path
\[
  p=\left[(\startmain,\,\mathbf0),\,(n_1,\,d_1),\,\dots,\,(n_k,\,d_k)\right]
\]
 that starts with the entrypoint of the exploded supergraph, we compute the micro function $f_p$ that corresponds to $p$. The micro function consists of the composition of all individual micro functions with which the edges of $p$ are labeled:
\begin{align}
  f_p=\textsf{EdgeFn}((n_{k-1},\,d_{k-1}),\,(n_k,\,d_k))\,\circ\ldots\circ
      \textsf{EdgeFn}(\startmain,\,\mathbf0),\,(n_1,\,d_1))\,.
\end{align}

>>>>

\subsection{Terminology and Notation}
%We will start by introducing several concepts used by the IFDS and IDE analyses.
%\begin{mdelete}\mtodo{We already say (but less precisely) what a CFG is in the introduction.}
The \textit{control-flow graph} of a procedure is a directed graph whose nodes are instructions, and which contains an edge from $n_1$ to $n_2$ whenever
$n_2$ may execute immediately after $n_1$. A CFG has a distinguished \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$.
Following the presentation of \cite{reps1995precise,sagiv1996precise}, we follow every
call instruction with a no-op instruction, so that every \textit{call node} is immediately
followed by a \textit{return node} in the CFG.
%\end{mdelete}
%and edges represent transfer of control between the instructions during an execution of the program. 
%A control-flow graph has a unique start node, $\startmain$, which is the node corresponding to the program entrypoint.
%An \textit{intraprocedural} path is a path in a control-flow graph whose nodes are in the same procedure. By contrast, an \textit{interprocedural path} is one that contains nodes from different procedures. 
The \textit{control-flow supergraph} of a program contains the CFGs of all of the procedures as
subgraphs. In addition, for each call instruction $c$, the supergraph contains a \textit{call-to-start} edge to the start node of every procedure that
may be called from $c$, and an \textit{end-to-return} edge from the end node of the procedure back to the call instruction.
%\otodo{do we really need to extra "return nodes" that the IFDS/IDE papers add?}
%is a control-flow graph
%in which each procedure $p$ is augmented with an additional \textit{start node} \textsf{start}$_p$ and \textit{end node} \textsf{end}$_p$, and for each call $c_q$ to a procedure $q$, there is a \textit{call node} \textsf{call}$_{c_q}$ and subsequent \textit{return node} \textsf{return}$_{c_q}$.

%A control-flow supergraph allows us to model the control flow in interprocedural paths.
 %The flow from the caller to the callee is represented using an edge \[(\textsf{call}_{c_q},\,\textsf{start}_q)\,.\] The control flow from the callee back to the caller goes through an edge \[(\textsf{end}_q,\,\textsf{return}_{c_q})\,.\]

@@

%arrow description
    \node [description] (intra_arrow_left) [above right = \dist and 2*\dist of st_secret] {};
    \node [description] (intra_arrow_right) [right = \dist of intra_arrow_left] {};
    \node [description] (inter_arrow_left) [below = .5*\dist of intra_arrow_left] {};
    \node [description] (inter_arrow_right) [below = .5*\dist of intra_arrow_right] {};
    \path[->](intra_arrow_left) edge node[right = .5*\dist]{intraprocedural edge} (intra_arrow_right);
    \path[dashed,->](inter_arrow_left) edge node[right = .5*\dist]{interprocedural edge} (inter_arrow_right);
\end{tikzpicture}
}
  \caption{An example supergraph for Listing~\ref{list:examplejava}}%
  \label{fig:examplesupergraph}%
  \end{figure}
\end{example}
}

@@

%Let each call node in a program be labeled with a distinct opening parenthesis and the corresponding return node with the matching closing parenthesis. For a given path $p$, let $s$ be the string that is obtained by concatenating the labels of the nodes in $p$.
%Then $p$ is \textit{valid} if $s$ belongs to the language of substrings of balanced parentheses. The set of all interprocedurally valid paths from the start node to a node $n$ is denoted as $\ivp(n)$. The set $\ivp(n)$ is a conservative approximation of all concrete execution paths from the start node to $n$.

%A \textit{context-sensitive} data-flow analysis is an analysis that considers only interprocedurally valid paths.

@@

However, the graph also contains an interprocedurally invalid path
  \[
    p_2=\left[\highlight{\textsf{call}_\texttt{f}}{lightsalmonpink},\,
          \highlight{\textsf{start}_\texttt{f}}{lightsalmonpink},\,
          \highlight{\texttt{if (s == null)}}{lightsalmonpink},\,
          \highlight{\texttt{return s}}{lightsalmonpink},\,
          \highlight{\textsf{end}_\texttt{f}}{lightsalmonpink},\,
          \highlight{\textsf{return}_\texttt{A.f}}{greyblue}
    \right]
  \]
  with corresponding string $\langle\}$.
\end{example}
\end{mdelete}
}

@@

\subsection{IFDS}\label{sec:bgifds}
The IFDS framework~\cite{reps1995precise} is a precise and efficient algorithm for data-flow analysis
%. IFDS was developed in 1995 by T.\,Reps, S.\,Horwitz, and M.\,Sagiv at the University of Wisconsin and
that has been used to solve a variety of data-flow analysis problems~\cite{bodden2013spl,naeem2008typestate,DBLP:conf/birthday/KreikerRRSWY13,tripp2009taj}.
%\mtodo{ The four references take away space in the References section. Remove some of them?  }
The IFDS framework is an instance of the \textit{functional approach} to data-flow analysis~\cite{pnueli1981two}
because it constructs summaries of the effects of called procedures.
\commentout{The IFDS analysis is a version of the classic \textit{functional approach} to data-flow analysis proposed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}.}
\commentout{In other data-flow algorithms not based on the functional approach, the result of the analysis at the entry of a procedure ``merges'' the incoming data obtained from all callers of the procedure. As a consequence, there is one global data-flow result computed at the end of the procedure. Context-sensitivity, however, allows an analysis to compute the data-flow result for a given procedure as a \textit{function} of the data-flow value at the start of the procedure. 
In other words, the analysis result for a procedure varies depending on where the procedure was called from. This significantly improves the precision of a data-flow analysis, which is why context-sensitivity is an important advantage of IFDS over classic data-flow algorithms.}
The IFDS framework is applicable to \textit{interprocedural} data flow problems whose domain is \textit{subsets} of a \textit{finite} set $D$,
and whose data-flow functions are \textit{distributive}.
A function $f$ is distributive if 
$f(x_1\sqcap x_2)=f(x_1)\sqcap f(x_2)$.

%The IFDS algorithm is applicable to problems which can be expressed with data-flow functions that satisfy certain restrictions. \textit{Interprocedural} flow functions specify how data flows from the invocation of a procedure to its start, and from the procedure's end back to its call site. \textit{Distributive} flow functions are those that distribute over the confluence operator. In the context of IFDS, the confluence operator is called meet, and it can be either union or intersection. The data-flow facts on which the analysis operates must be a \textit{finite} set $D$. Each flow function operates on a \textit{subset} of $D$ (for example, the set of variables in the program) which makes the domain of the flow functions the power set of $D$.

\commentout{The purpose of the IFDS framework is to solve a special subset of interprocedural, flow-sensitive, context-sensitive data-flow-analysis problems. The main idea of IFDS is to encode the data-flow analysis problem into a graph-reachability problem.}

@@

The flow functions $F$ define the edges of the exploded supergraph.
Using the flow functions, the IFDS algorithm computes the interprocedurally \textit{realizable} paths from the start to the rest of the exploded graph's nodes. A realizable path is a valid path in the exploded supergraph that starts with the entry node $\startmain$.

@@

The IDE framework is an expressive extension to IFDS that was created by the same authors in 1996.
The problems that IDE can solve include, but are not limited to, IFDS problems~\cite{reps1995precise}. Just as the IFDS algorithm, the IDE algorithm is suitable for data-flow analyses that can be encoded with interprocedural, distributive flow functions. However, in IDE, the domain of the flow functions is not restricted to sets $D$ of data-flow facts. The IDE domain of a flow function consists of \textit{environments} that map data-flow facts from the set $D$ to lattice elements.

@@

The IDE algorithm~\cite{sagiv1996precise} extends IFDS to
\textit{interprocedural} \textit{distributive} \textit{environment}
problems. An \textit{environment} problem is an analysis whose dataflow
lattice is the lattice $\textsf{Env}(D,L)$ of maps from a finite set $D$ to a meet semilattice
$L$ of finite height, ordered pointwise. Like IFDS, IDE requires the dataflow functions to be distributive.

@@

\mtodo{I think the rest of this section will not make sense to anyone who does not already understand it. Should I try to replace it with one paragraph that tries to give an intuitive understanding of what the IDE algorithm is doing?}
The overall idea behind computing the lattice elements $l_{n,\,d}$ is the following. For each interprocedurally realizable path
\[
  p=\left[(\startmain,\,\mathbf0),\,(n_1,\,d_1),\,\dots,\,(n_k,\,d_k)\right]
\]
 that starts with the entrypoint of the exploded supergraph, we compute the micro function $f_p$ that corresponds to $p$. The micro function consists of the composition of all individual micro functions with which the edges of $p$ are labeled:
\begin{align}
  f_p=\textsf{EdgeFn}((n_{k-1},\,d_{k-1}),\,(n_k,\,d_k))\,\circ\ldots\circ
      \textsf{EdgeFn}(\startmain,\,\mathbf0),\,(n_1,\,d_1))\,.
\end{align}

### 2014-12-17 content/eval.tex
pass through section 3
inter- and intra-procedural to interprocedural and intraprocedural

\begin{odelete}
\subsubsection{IFDS}
\otodo{We should incorporate the four functions into the explanation of IFDS in the background. Then we don't need them here.}
As described in Section~\ref{sec:ifdsdef}, an IFDS problem is defined in terms of an exploded supergraph. The control-flow supergraph of an input program can be retrieved using WALA. Hence, our implementation of an IFDS problem should be able to convert a control-flow supergraph into an exploded supergraph.

We represent an IFDS problem with a trait, or protocol, that contains declarations of four \textit{flow functions}. Each function has type 
\[
  F:\,(N\times D\times N)\to2^D
\]
and defines a set of edges on the exploded graph. 
Given an edge $(n_1,\,n_2)$ of the control-flow supergraph and the fact $d_1$ that 
corresponds to the source node $n_1$, $F(n_1,\,d_1,\,n_2)$ returns the set of all facts $d_2\in D_2$ such that $((n_1,\,d_1),\,(n_2,\,d_2))\in E^\#$\footnote{In each invocation of a flow function, the fact $d_1$ is provided by the IDE algorithm.}.
The four functions are:
\begin{itemize}
  \item \textsf{call-start}, for inter-procedural edges from a call node to the start node of the target method;
  \item \textsf{call-return}, for intra-procedural edges from a call node to its return node;
  \item \textsf{end-return}, for inter-procedural edges from the end node of a method to the return node of the callee;
  \item \textsf{default}, for all other intra-procedural edges.
\end{itemize}
\end{odelete}

@@

Given an IFDS problem described with IFDS flow functions, an equivalence transformation creates an IDE problem described with the following IDE flow functions:
\begin{align*}
  \textsf{call-start}^\equiv(n_1,\,d_1,\,n_2)=&\{(d_2,\,\epsilon(d_1,\,d_2))\,|\,d_2\in\textsf{call-start}(n_1,\,d_1,\,n_2)\}\\
  \textsf{call-return}^\equiv(n_1,\,d_1,\,n_2)=&\{(d_2,\,\epsilon(d_1,\,d_2))\,|\,d_2\in\textsf{call-return}(n_1,\,d_1,\,n_2)\}\\
  \textsf{end-return}^\equiv(n_1,\,d_1,\,n_2)=&\{(d_2,\,\epsilon(d_1,\,d_2))\,|\,d_2\in\textsf{end-return}(n_1,\,d_1,\,n_2)\}\\
  \textsf{default}^\equiv(n_1,\,d_1,\,n_2)=&\{(d_2,\,\epsilon(d_1,\,d_2))\,|\,d_2\in\textsf{default}(n_1,\,d_1,\,n_2)\}\,,
\end{align*}
where $\epsilon$ is the bottom function on an edge from a $\Lambda$-fact to a non-$\Lambda$-fact, and the identity function otherwise:
\[
  \epsilon(d_1,\,d_2)=\begin{cases}
    \lambda l\,.\,\bot&\text{if $d_1=\Lambda$ and $d_2\ne\Lambda$;}\\
    \id&\text{otherwise.}
  \end{cases}
\]

@@

We tested the propagation of constants on different intra- and inter-procedural data-flow paths, in parameter passing,
and in conditional branches. Each regression test contained assertions of the form ``at the end of method $m$, variable with name $x$ should be (not) constant''.

@@

\begin{figure}
  \centering
  \begin{minipage}{\textwidth}
    \inputMinted{java}{interprocRec.java}
  \end{minipage}
  \caption{Inter-procedurally-correlated calls}
  \label{list:interProcRec}
\end{figure}

Another constraint of the algorithm is that it only accounts for intra-procedurally-correlated receivers, or receivers on which correlated calls occur within one method. For example, in Listing~\ref{list:interProcRec}, \verb'a' is a correlated-call receiver, since there are two polymorphic method invocations on \verb'a'. However, the first one, \verb'a.setString()', is inside method \verb'main', and the second one, \verb'a.printString()', is inside method \verb'propagate'. Therefore, we do not treat \verb'a' as a correlated-call receiver, and the analysis would not improve the original IFDS result for this program.

>>>>

\commentout{
\begin{odelete}
\subsubsection{IFDS}
\otodo{We should incorporate the four functions into the explanation of IFDS in the background. Then we don't need them here.}
As described in Section~\ref{sec:ifdsdef}, an IFDS problem is defined in terms of an exploded supergraph. The control-flow supergraph of an input program can be retrieved using WALA. Hence, our implementation of an IFDS problem should be able to convert a control-flow supergraph into an exploded supergraph.

We represent an IFDS problem with a trait, or protocol, that contains declarations of four \textit{flow functions}. Each function has type 
\[
  F:\,(N\times D\times N)\to2^D
\]
and defines a set of edges on the exploded graph. 
Given an edge $(n_1,\,n_2)$ of the control-flow supergraph and the fact $d_1$ that 
corresponds to the source node $n_1$, $F(n_1,\,d_1,\,n_2)$ returns the set of all facts $d_2\in D_2$ such that $((n_1,\,d_1),\,(n_2,\,d_2))\in E^\#$\footnote{In each invocation of a flow function, the fact $d_1$ is provided by the IDE algorithm.}.
The four functions are:
\begin{itemize}
  \item \textsf{call-start}, for interprocedural edges from a call node to the start node of the target method;
  \item \textsf{call-return}, for intraprocedural edges from a call node to its return node;
  \item \textsf{end-return}, for interprocedural edges from the end node of a method to the return node of the callee;
  \item \textsf{default}, for all other intraprocedural edges.
\end{itemize}
\end{odelete}
}

@@

Given an IFDS problem described with IFDS flow functions, an equivalence transformation creates an IDE problem described with the following IDE flow functions:
\begin{align*}
  \textsf{call-start}^\equiv(n_1,\,d_1,\,n_2)=&\{(d_2,\,\epsilon(d_1,\,d_2))\,|\,d_2\in\textsf{call-start}(n_1,\,d_1,\,n_2)\}\\
  \textsf{call-return}^\equiv(n_1,\,d_1,\,n_2)=&\{(d_2,\,\epsilon(d_1,\,d_2))\,|\,d_2\in\textsf{call-return}(n_1,\,d_1,\,n_2)\}\\
  \textsf{end-return}^\equiv(n_1,\,d_1,\,n_2)=&\{(d_2,\,\epsilon(d_1,\,d_2))\,|\,d_2\in\textsf{end-return}(n_1,\,d_1,\,n_2)\}\\
  \textsf{default}^\equiv(n_1,\,d_1,\,n_2)=&\{(d_2,\,\epsilon(d_1,\,d_2))\,|\,d_2\in\textsf{default}(n_1,\,d_1,\,n_2)\}\,,
\end{align*}
where $\epsilon$ is the bottom function on an edge from a $\mathbf0$-fact to a non-$\mathbf0$-fact, and the identity function otherwise:
\[
  \epsilon(d_1,\,d_2)=\begin{cases}
    \lambda l\,.\,\bot&\text{if $d_1=\mathbf0$ and $d_2\ne\mathbf0$;}\\
    \id&\text{otherwise.}
  \end{cases}
\]

@@

We tested the propagation of constants on different intra- and interprocedural data-flow paths, in parameter passing,
and in conditional branches. Each regression test contained assertions of the form ``at the end of method $m$, variable with name $x$ should be (not) constant''.

@@

\begin{figure}
  \centering
  \begin{minipage}{\textwidth}
    \inputMinted{java}{interprocRec.java}
  \end{minipage}
  \caption{Interprocedurally-correlated calls}
  \label{list:interProcRec}
\end{figure}

Another constraint of the algorithm is that it only accounts for intraprocedurally-correlated receivers, or receivers on which correlated calls occur within one method. For example, in Listing~\ref{list:interProcRec}, \verb'a' is a correlated-call receiver, since there are two polymorphic method invocations on \verb'a'. However, the first one, \verb'a.setString()', is inside method \verb'main', and the second one, \verb'a.printString()', is inside method \verb'propagate'. Therefore, we do not treat \verb'a' as a correlated-call receiver, and the analysis would not improve the original IFDS result for this program.
